---
title: "bayesian linear regression"
output: html_notebook
---

# Data Preprocessing
the data set used is about medical cost personal
the following are the variabels contained in the data

* age: age of primary beneficiary

* sex: insurance contractor gender, female, male

* bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height, objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

* children: Number of children covered by health insurance / Number of dependents

* smoker: Smoking

* region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

* charges: Individual medical costs billed by health insurance

importing data
```{r}
data <-  read.csv("https://github.com/novalsaputra/val_proj/raw/master/bayesian-linear-regression-in-r/data/insurance.csv",head=TRUE)
str(data)
```

importing packages 
```{r}
library(PerformanceAnalytics)
library(ggplot2)
```

```{r}
plot((data$charges))
```


