---
title: "bayesian linear regression"
output: html_notebook
---

# Data Preprocessing
the data set used is about medical cost personal
the following are the variabels contained in the data

* age: age of primary beneficiary

* sex: insurance contractor gender, female, male

* bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height, objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

* children: Number of children covered by health insurance / Number of dependents

* smoker: Smoking

* region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

* charges: Individual medical costs billed by health insurance

importing data
```{r}
insurance <-  read.csv("https://github.com/novalsaputra/val_proj/raw/master/bayesian-linear-regression-in-r/data/insurance.csv",head=TRUE)
str(insurance)
```
```{r}
summary(insurance)
```


importing packages 
```{r}
library(ggplot2)
library(gridExtra)
```

```{r}
plot.age <- ggplot(insurance, aes(x = age, y = charges)) +
 geom_point()

plot.bmi <- ggplot(insurance, aes(x = bmi, y = charges)) +
 geom_point()

grid.arrange(plot.age, plot.bmi, ncol=2)
```
```{r}
age1 <- ggplot(insurance, aes(x = age, y = charges,col=sex)) + geom_point()
age2 <- ggplot(insurance, aes(x = age, y = charges,col=bmi)) + geom_point()
age3 <- ggplot(insurance, aes(x = age, y = charges,col=children)) + geom_point()
age4 <- ggplot(insurance, aes(x = age, y = charges,col=smoker)) + geom_point()
age5 <- ggplot(insurance, aes(x = age, y = charges,col=region)) + geom_point()
grid.arrange(age1,age2,age3,age4,age5,ncol=2)
```

```{r}
ggplot(insurance, aes(x = age, y = charges,col=smoker)) + geom_point()
```
```{r}
bmi1 <- ggplot(insurance, aes(x = bmi, y = charges,col=sex)) + geom_point()
bmi2 <- ggplot(insurance, aes(x = bmi, y = charges,col=age)) + geom_point()
bmi3 <- ggplot(insurance, aes(x = bmi, y = charges,col=children)) + geom_point()
bmi4 <- ggplot(insurance, aes(x = bmi, y = charges,col=smoker)) + geom_point()
bmi5 <- ggplot(insurance, aes(x = bmi, y = charges,col=region)) + geom_point()
grid.arrange(bmi1,bmi2,bmi3,bmi4,bmi5,ncol=2)
```

```{r}
ggplot(insurance,aes(x=bmi,y=charges,col=smoker)) + geom_point()
```

```{r}
plot.sex <- ggplot(insurance, aes(x = sex, y = charges)) +
 geom_boxplot()

plot.smoker <- ggplot(insurance, aes(x = smoker, y = charges)) +
 geom_boxplot()

plot.child <- ggplot(insurance, aes(x = as.factor(children), y = charges)) +
 geom_boxplot()

plot.region <- ggplot(insurance, aes(x = region, y = charges)) +
 geom_boxplot()

grid.arrange(plot.sex, plot.smoker, plot.child, plot.region, ncol=2, nrow=2)

```


# Ordinary Regression

```{r}
mod <- lm(charges ~ . ,data=insurance)
summary(mod)
```

```{r}
#m <- lm(charges~age*bmi*children*smoker*region*smoker*bmi)
#sm <- step(m)
#summary(sm)
#terlalalu komplit
```

final model used
```{r}
mod2 <- lm(charges ~ age + bmi + children + smoker + region + smoker*bmi, data=insurance)
summary(mod2)
```
# OLS with matrix

```{r}
#variabel definition
attach(insurance)
y <- charges
x1 <- age
x2 <- sex
x3 <- bmi
x4 <- children
x5 <- smoker
x6 <- region

#dummy for x6
x6a <- as.integer(x6a)
x6b <- as.integer(x6b)
x6c <- as.integer(x6c)

x1x5 <- age*as.numeric(smoker)
x3x5 <- bmi*as.numeric(smoker)
```

```{r}
mod <- lm(y ~ x1+x2+x3+x4+x5+x6a+x6b+x6c+x1x5+x3x5)
summary(mod)
```


```{r}
mod1 <- lm(y ~ x1+x2+x3+x4+x5+x6+x1x5 + x3x5)
summary(mod1)
```


# Inference Parameter linear Regression with Bayesian Approach

```{r}
mod2 <- lm(y ~ x1+ x3 + x4 +x5 +x6 +x3x5)
summary(mod2)
```
```{r}
x6 <- region
x6a <- as.integer(rep(0,length(x6)))
x6b <- as.integer(rep(0,length(x6)))
x6c <- as.integer(rep(0,length(x6)))

for (i in 1:length(x6)){
  if (x6[i]=="northwest"){
    x6a[i] = 1
  }
  else if (x6[i]=="southeast"){
    x6b[i] = 1
  }
  else if (x6[i]=="southwest"){
    x6c[i] =1
  }
  else {
    x6a[i] = 0
    x6b[i] = 0
    x6c[i] = 0
  }
}

table(x6a)
table(x6b)
table(x6c)
```

```{r}
X <- as.matrix(cbind(rep(1,length(y)),x1,x3,x4,x5,x6a,x6b,x6c,x3x5))
dim(X)
```



```{r}
n <- dim(X)[1]
p <- dim(X)[2]
```


```{r}
#prior parameter
nu0 <- 1
s20 <- summary(mod2)$sigma^2 #prior variation from ols
g <- n
S <- 1000
```

```{r}
#posterior calclation
Hg <- (g/(g+1))*X%*%solve(t(X)%*%X)%*%t(X)
SSRg<- t(y)%*%(diag(1,nrow=n)-Hg)%*%y

Vbeta <- g*solve(t(X)%*%X)/(g+1)
Ebeta <- Vbeta %*% t(X) %*% y

```


```{r}
#monte Carlo

n<-dim(X)[1]
p<-dim(X)[2]
Hg<-(g/(g+1))*X%*%solve(t(X)%*%X)%*%t(X)
SSRg<- t(y)%*%(diag(1,nrow=n)-Hg)%*%y
s2<-1/rgamma(S,(nu0+n)/2,(nu0*s20+SSRg/2)) #gamma sample
Vb<-g*solve(t(X)%*%X)/(g+1)
Eb<-Vb%*%t(X)%*%y
E<- matrix(rnorm(S*p,0,sqrt(s2)),S,p) #sample beta
```

```{r}
beta<-t(t(E%*%chol(Vb))+c(Eb))
```

```{r}
b <- colSums(beta)/S

b
```

```{r}
ycap <- X%*%c(b)
bys <- data.frame(y,ycap)
ggplot(bys,aes(y,abs(y-ycap))) +
        geom_point()+
        geom_smooth()
```

```{r}
ggplot(bys) + geom_smooth(aes(x=y,y=ycap))
```


```{r}
library(tidyr)
library(dplyr)
library(ggplot2)

signif = apply(beta, MARGIN = 2, FUN = quantile, probs = c(0.025, 0.5, 0.975)) %>%
  apply(MARGIN = 2, FUN = function(y) !(y[1] < 0 && 0 < y[3]))

beta_df = as.data.frame(beta) %>%
  gather(key = 'variable', val = 'coefficient') %>%
  mutate(signif = signif[variable])

ggplot(beta_df, aes(x = variable, y = coefficient, color = signif)) +
  stat_summary(fun.y = mean, fun.ymin = function(y) quantile(y, probs = c(0.025)), fun.ymax = function(y) quantile(y, probs = c(0.975))) +
  geom_hline(yintercept = 0, lty = 2)
```

